Implicit assumptions and their impact on photometric redshift PDF performance in the context of LSST

### 2018-11-29 paper/tex/methods.tex
address comment on line 688

\begin{equation}
\beta_{i }(\x) =  \mathbb{E}\left[\phi_i(z)|\x\right] \equiv \int f(z|\x)   \phi_i(z) dz. \label{eq:FlexZBoost_coeffs}
\end{equation}
These coefficients can easily be estimated from data by regression.

@@

\begin{equation}
x_{u} = \mu_{u}+\Sigma_{uo}\Sigma_{oo}^{-1}(x_{o}-\mu_{o}),
\end{equation}  %\]
where the subscript $o$ in $x_{o}$ indexes the \emph{observed} part of the input $x$, whereas the subscript $u$ indexes the \emph{unobserved} set (similarly for $\mu$ and $\Sigma$). This is the optimal expected value of the unobserved variables given the observed ones if the distribution is jointly Gaussian, note that if the variables are independent, i.e. $\Sigma_{uo}=0$, this will reduce to a simple average predictor.  We use the Variable Covariance (VC) option in \textsc{GPz} with 200 basis functions after we note that there is no significant increase in the performance on the validation set (using 80\%-20\% training-validation split) and with no cost-sensitive learning applied.

>>>>

\begin{equation}
\beta_{i }(\x) =  \mathbb{E}\left[\phi_i(z)|\x\right] \equiv \int f(z|\x)   \phi_i(z) dz. \label{eq:FlexZBoost_coeffs}
\end{equation}
These coefficients can easily be estimated from data by regression since $\mathbb{E}\left[\phi_i(z)|\x\right]$ is the regression of $\phi_i(z)$ (a transformation of $Z$) on $X$.

@@

\begin{equation}
x_{u} = \mu_{u}+\Sigma_{uo}\Sigma_{oo}^{-1}(x_{o}-\mu_{o}),
\end{equation}  %\]

where the subscript $o$ in $x_{o}$ indexes the \emph{observed} part of the input $x$, whereas the subscript $u$ indexes the \emph{unobserved} set (similarly for $\mu$ and $\Sigma$). This is the optimal expected value of the unobserved variables given the observed ones if the distribution is jointly Gaussian, note that if the variables are independent, i.e. $\Sigma_{uo}=0$, this will reduce to a simple average predictor.  We use the Variable Covariance (VC) option in \textsc{GPz} with 200 basis functions after we note that there is no significant increase in the performance on the validation set (using 80\%-20\% training-validation split) and with no cost-sensitive learning applied.
